Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2013-01-05 chi2013-webbox.tex
mor etext

We hypothesise that end-users will benefit from tools that allow them to effectively browse, use and consume heterogeneous structured data from diverse sources. In this paper, we present an investigation into extending PIM tools to effectively use emerging ecosystems of personal data.  We used a three-stage sequential exploratory mixed-method approach: first, we performed a semi-structured interview pre-study to understand the types of tasks people performed using multiple information sources, and the processes that they relied upon to perform such tasks.  Our results suggested that people routinely drew upon multiple and diverse sources for reasons including coverage, reliability, and to gain multiple perspectives or subjective assessments.

>>>>

% We hypothesise that end-users will benefit from tools that allow them to effectively browse, use and consume heterogeneous structured data from diverse sources. 
In this paper, we present an investigation into ways that PIM tools might be extended to allow data to be brought in in an ad-hoc fashion from any structured data source, combined with other data, and interrogated to effectively allow end-user citizens to harness knowledge from the vast, emerging and future ecosystems of personal data.  We used a three-stage sequential exploratory mixed-method approach in this investigation: first, we performed a semi-structured interview pre-study to understand the types of tasks people performed using multiple information sources, and the processes that they relied upon to perform such tasks.  Our results suggested that people routinely drew upon multiple and diverse sources for reasons including coverage, reliability, and to gain multiple perspectives or subjective assessments.
